Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-24 demystify.tex
updates

While I am not an international student, many of my students and collaborators are international.  I also mentor many students from Vietnam.  I also have many colleague and friends who were international students and have heard their stories.  I hope to capture their challenges and experiences in this document so that it can be useful for prospective international students.

\paragraph{Acknowledgement} Many people have contributed to this document.
Profs. Craig Yu (GMU), Hakan Aydin (GMU), 
Xiaokuan Zhang (GMU), and Hung Le (UMass) provided valuable input in the early version. Other GMU faculty members also have provided feedback and contributions.  Many students including Didier (GMU), Thanh (Melbourne), and Dat (Melbourne) have contributed valuable questions and feedback. 
\textbf{Thank you!}

>>>>

While I am not an international student, many of my students and collaborators are international.  I also mentor multiple students from Vietnam.  I also have various colleague and friends who were international students and have heard their stories.  I hope to capture their challenges and experiences in this document so that it can be useful for prospective international students.

\paragraph{Acknowledgement} Many people have contributed to this document.
Profs. Craig Yu (GMU), Hakan Aydin (GMU), 
Xiaokuan Zhang (GMU), Hung Le (UMass), and Deepak Kapur (UNM) provided valuable input in the early version. Other GMU faculty members also have provided feedback and contributions.  Many students including Didier (GMU), Thanh (Melbourne), and Dat (Melbourne) have contributed valuable questions and feedback.
\textbf{Thank you!}
